---
title: "HW 09 - Bootstrapping the GSS"
author: "Team yiit"
date: "2018-11-03"
output: github_document
---

### Load packages

```{r load-packages, message=FALSE}
library(infer)
library(tidyverse)
library(readr)
library(stringr)
```

### Load data

```{r load-data, message=FALSE}

gss2016 <- read_csv("gss2016.csv", guess_max = )

```

### Set seed

```{r set-seed}
set.seed(12354)
```

### Exercise 1

```{r}
gss2016 %>%
  count(harass5)
```

The possible responses to this question are Does not apply (i do not have a job/superior/co-worker), Don't know, No, No answer, Not applicable, and Yes. The number of people who said each response is 96, 1, 1136, 7, 1390, and 237 respectively.

### Exercise 2

```{r filter-harass5}
harassed <- gss2016 %>%
  filter(harass5 == "Yes" | harass5 == "No")
```

### Exercise 3

```{r harass5-prop}
harassed %>%
  group_by(harass5) %>%
  summarise(n = n()) %>%
  mutate(prop = scales::percent(n / sum(n)))
```

82.7% of respondents for whom this question is applicable to have been harassed by their superiors or co-workers at their job.

### Exercise 4

```{r visualize-bootstrap}

harass_bs <- 
  harassed %>%
    specify(response = harass5, success = "Yes") %>% 
    generate(reps = 1000, type = "bootstrap") %>% 
    calculate(stat = "prop")

harass_bs

ggplot(data = harass_bs, 
       mapping = aes(x = stat)) +
  geom_histogram(binwidth = 0.005, 
                 fill = "Grey", 
                 color = "Black") +
  labs(title = "Americans who have been harassed at work",
       subtitle = "Bootstrap distribution of proportions",
       x = "Proportion",
       y = "Count")

```

### Exercise 5

```{r harass5-confint}
harass_bs %>%
  summarise(
    lower = quantile(stat, 0.025),
    upper = quantile(stat, 0.975),
    )
```

The 95% bootstrap confidence interval based on the distribution we constructed above is 0.152 to 0.192.


### Exercise 6

We are 95% confident that the median percentage of those who have been harassed by their superiors or co-workers at their job is between 15.2% and 19.2%.

### Exercise 7

To be 95% confident means that that there is a 95% chance that the confidence interval determined contains the true value of the proportion of Americans who are harassed at work. We can say with 95% confidence, or certainty, that the true percentage of Americans who are harassed at work lies within our confidence interval.

### Exercise 8

90% confidence interval: (0.157, 0.189)

99% confidence interval: (0.147, 0.196)

If the confidence that our interval contains the true proportion of Americans who are harassed at work increases, then the interval must become wider, and vice versa. This is because as the interval widens to cover more potential proportion values, there is a greater probability (or confidence) that it contains the true proportion.

### Exercise 9

```{r email-weekly}

gss2016 <- gss2016 %>%
  mutate(email = 60*as.numeric(emailhr) + as.numeric(emailmin)) 

```

### Exercise 10

```{r no-NA-email}
non_NA_email <- gss2016 %>%
  select(email) %>%
  filter(is.na(email) == FALSE)
```

### Exercise 11

```{r non-na-visualization}

ggplot(data = non_NA_email, 
       mapping = aes(x = email)) +
  geom_histogram(binwidth = 500, 
                 fill = "Grey", 
                 color = "Black") +
  labs(title = "Distribution of Email Time",
       x = "Email Time (min)",
       y = "Count")

non_NA_email %>%
  summarise(med = median(email), 
            mean = mean(email))

```

The media is a preferrable measure of the amount of time Americans spend using email, because the distribution of time spent on email is right skewed, and the median statistic is able to be insensitive to skew whereas mean is not.

### Exercise 12

Bootstrapping is used to estimate a statistic that describes the amount of time that all Americans spend using email weekly. It does this by creating a bootstrap distribution of medians using several samples from the email data, and then creating a confidence interval that estimates the true population median to a given degree of certainty/confidence.

### Exercise 13

```{r confidence-interval-email}

email_bs <- non_NA_email %>%
  specify(response = email) %>% 
  generate(reps = 1000, 
           type = "bootstrap") %>% 
  calculate(stat = "median")

email_bs

email_bs %>%
summarize(lower = format(round(quantile(stat, 0.05), 4), nsmall = 4),
upper = format(round(quantile(stat, 0.95), 4), nsmall = 4))

```

The 90% confidence interval is (120, 120). This means that we can say with 90% confidence that the median time that American workers spend using email is 2 hours per week. The calculated confidence interval has the same upper and lower bounds most likely because 120 was a modal value in the original data, meaning that many individuals spent 2 hours per week, such that a confidence interval with 90% confidence would suggest that Americans spend 2 hours per week on email.

### Exercise 14

```{r exercise14}
gss2016 <- mutate(gss2016, educ = as.integer(gss2016$educ))


gss_noNA <- gss2016 %>%
  select(educ, born) %>%
  filter(born != "No answer") %>%
  filter(is.na(educ) == "FALSE")



boot_meandiff <- gss_noNA %>%
  specify(response = educ, explanatory = born) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c(born = "Yes", born = "No"))

ggplot(data = boot_meandiff, 
       mapping = aes(x = stat)) +
  geom_histogram(binwidth = 0.1, 
                 fill = "Grey", 
                 color = "Black") +
  labs(title = "Difference in mean years of education for those born and not born in the US",
       x = "Difference in mean years of education",
       y = "Count")

boot_meandiff %>%
  summarise(quantile(stat, 0.005), 
            quantile(stat, 0.995))


```

We can say with 99% confidence, or certainty, that the difference in mean years of education for those born and not born in the US lies between 0.166 and 1.26.


### Exercise 15

```{r politics}

gss2016 <- mutate(gss2016, science = case_when(
  advfront == "Agree" | advfront == "Strongly agree"           ~ "Yes", 
  advfront == "Disagree" | advfront == "Strongly disagree"       ~ "No"
))

```



### Exercise 16

```{r pol_sides}
gss2016 <- mutate(gss2016, polside = case_when(
  polviews == "Liberal" | polviews == "Extremely liberal" | polviews == "Slightly liberal"          ~ "Liberal", 
  polviews == "Conservative" | polviews == "Extrmly conservative" | polviews == "Slghtly conservative" ~ "Conservative" 
))

```

### Exercise 17

```{r filter_politics}
politics_filtered <- gss2016 %>%
  select(polside, science) %>%
  drop_na(polside) %>%
  drop_na(science)


```



### Exercise 18


Bootstrapping will take random and equally sized samples of the difference in proportion of liberals and not liberals who think that science research is necessary. It does this many times with replacement and will eventually provide a data set of difference in proportions. We can examine the distribution of the data set and calculate a confidence interval that estimates the true population median to a given degree of certainty/confidence.


### Exercise 19

```{r}

```


